Refinement of Thermostated Molecular Dynamics Using Backward Error Analysis

### 2018-11-11 rigid_bodies.tex
Revision of concluding remarks

In this paper, we have devised a general approach that integrates backward error analysis into the Nos\'{e}-Hoover chains and global stochastic thermostats.
The key rationale behind our proposal came from recognizing that a Shadow kinetic energy should substitute the specified one in the equations dictating the thermostat action.
This turns out to be crucial for simulations that display considerable discretization errors, as a ``clear definition of simulation temperature''\cite{Eastwood_2010} is obtained by applying Tolman's generalized equipartition theorem to a Shadow kinetic energy.

A significant enhancement was achieved for a system of TIP3P rigid water molecules\cite{Jorgensen_1983} by using an analytically approximation to the Shadow Hamiltonian (here referred to as \textit{refined Hamiltonian}) with a minimal computational overhead, and whose derivation was greatly facilitated by the unsplit solution of rotation introduced in our previous paper\cite{Silveira_2017}.
Particularly, we have been able to remove the serious artifacts observed in the schemes of Martyna \textit{et al}. \cite{Martyna_1996} and Kamberaj \textit{et al}. \cite{Kamberaj_2005}, correcting the discretization effects in numerically computed averages for time-step sizes up to $5~\text{fs}$.
From our rigorous analysis of these schemes, we would not recommend a time-step size larger than $1~\text{fs}$.
The fact of having overcome that barrier is of paramount importance as allows us to actually exploit the high numerical stability provided by rigid-body MD.

Finally, it should be remarked that our method is not limited to rigid-body MD. It could be employed, for instance, in conjuction with other constrained MD schemes, such as SHAKE\cite{Ryckaert_1977} and RATTLE\cite{Andersen_1983}.
Of course, restrictions arising from these methods must be properly taken into account, as we did for the quaternion time-derivative.

>>>>

In this paper, we have devised a general approach that integrates backward error analysis into Nos\'{e}-Hoover chains and other global thermostats.
The rationale for our proposal arises from recognizing that a ``shadow kinetic energy'' should substitute the conventional one in the equations that dictate the thermostat action.
In practice, we employ backward error analysis to compute, with minimal computational overhead, a refined version of the kinetic energy, which serves as an estimate for its shadow analogue.
This turns out to be crucial for simulations that display considerable discretization errors, in which a clearer definition of the simulation temperature \cite{Eastwood_2010} is obtained by applying Tolman's generalized equipartition theorem to the refined kinetic energy rather than to the conventional one.

A significant enhancement was achieved for a system of rigid TIP3P-water molecules \cite{Jorgensen_1983}.
Analytical derivation of a refined Hamiltonian formula for rigid bodies was greatly facilitated by considering an unsplit integration of rotations, such as in the method we have recently introduced \cite{Silveira_2017}.
Particularly, we have been able to remove serious artifacts observed when using the method of Kamberaj, Low, and Neal \cite{Kamberaj_2005} or a rigid-body extension of the standard Nos\'{e}-Hoover chain thermostat \cite{Martyna_1992, Martyna_1996}.
The refinement/reweighting approach described in Sec.~\ref{sec:refined_method} corrected discretization effects in computed thermodynamic properties of water for time-step sizes up to $5~\text{fs}$.
Without the refinement, we would not recommend the use of time steps larger than $1~\text{fs}$.
Having overcome such barrier is of paramount importance as it allows one to actually exploit the high numerical stability and useful coarse-graining provided by rigid-body MD.

Finally, it is worth remarking that our method is not limited to rigid bodies.
It can be employed, for instance, in conjunction with other constrained MD schemes, such as SHAKE \cite{Ryckaert_1977} and RATTLE \cite{Andersen_1983}, for instance.
Of course, restraints arising from these methods must be properly taken into account, as done here for the time-derivatives of orientation quaternions.
